---
title: ""
author: "lmuehlen"
date: "`r Sys.Date()`"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Packages

```{r}

library(DataExplorer)
library(showtext)
library(ggbeeswarm)
library(countrycode)
library(ggthemes)
library(devtools)
library(fixest)
library(plm)
library(readxl)
library(countrycode)
library(tidyverse)
library(parsec)
library(OECD)
library(haven)
library(rdbnomics)
library(usethis)
library(patchwork)
library(scales)
library(psych)
library(reporttools)
library(devtools)
library(data.table)
library(sf)
library(eurostat)
library(imf.data)



devtools::source_gist("c4d1089a501d3567be9fb784b1c5a6ab") 
#loads functions of Sebastian Daza for creating descriptive tables

#usethis::use_github()
#library(lpdid)
source("Functions/lpdid.R")
source("Functions/get_poset_fiscalrules.R")
source("Functions/plot_lpdid.R")
source("Functions/save_vis.R")
```


Must be changed!!
```{r}
font_add("lmroman",regular="C:/Users/leona/AppData/Local/Microsoft/Windows/Fonts/lmroman10-regular.otf") 
showtext_auto()


f_graphics<-"C:/Users/leona/Dropbox/Apps/Overleaf/Fiscal Rules Budget Composition/Graphics"
```


# Fiscal rule index

## Import data

```{r eval=FALSE, warning=FALSE, include=FALSE}
imffr<-read_excel("Data/imf_fiscalrule_prepared.xlsx")%>%
  mutate(countrycode=countrycode(countryname,"country.name","iso3c",custom_match = c("Kosovo"="XXK")))%>%
  select(countrycode,everything())

```

## Index creation

First, I build a fiscal rules stringency index based on partially ordered set theory (POSET). For this, I use the parsec library. The four properties underlying the index of fiscal rules are defined as follows:

| Variable | Property           | Meaning values                                                                                                                        |
|:----------------|:-----------------|:------------------------------------|
| C1       | Monitoring         | 2= monitoring <br> 1=no monitoring <br> 0= no rule                                                                                    |
| C2       | Formal enforcement | 2 = formal enforcement procedures <br>1 = no formal enforcement procedures <br>0 = no rule                                            |
| C3       | Coverage           | 3 =general government<br>2 = general government (sim. rules other levels)<br>1 = central government <br> 0=no rule                    |
| C4       | legal basis        | 4= constitutional/international treaty <br> 3 = statutory basis<br>2 = coalition agreement<br>1 = political commitment <br> 0=no rule |

Note: We compute the indices of national and supranational fiscal rules separately and for the legal basis constitutional (5) is only for the national and international treaty (4) only for the supranational, therefore we redefine constitutional as 4.

```{r eval=FALSE, include=FALSE}
imffr2<-imffr%>%
  select(matches("index"),countrycode,countryname,year)%>%
  pivot_longer(-c(countrycode,countryname,year),names_pattern = "index_(.*)_(.*)_(.*)",names_to = c("dimension","level","ruletype"),values_to = "values")%>%
  pivot_wider(names_from = dimension,values_from = values)%>%
  mutate(monitoring=case_when(
                              monitoring==1~2,
                              monitoring==0~1,
                              TRUE~0),
         formalenforcement=case_when(
                              formalenforcement==1~2,
                              formalenforcement==0~1,
                              TRUE~0),
         legalbasis=case_when(
                              legalbasis==5~4,
                              is.na(legalbasis)~0,
                              TRUE~legalbasis),
         coverage=case_when(
                              coverage==2~3,
                              coverage==1.5~2,
                              coverage==1~1,
                              TRUE~0
         )
         )


index_variables<-list(
  monitoring=c(0,1,2),
  formalenforcement=c(0,1,2),
  legalbasis=c(0,1,2,3,4),
  coverage=c(0,1,2,3)
)

index1<-get_poset_fiscalrules(imffr2,index_variables)

ddpcr::quiet(
index2<-index1%>%summary()%>%select(monitoring,formalenforcement,legalbasis,coverage,av_rank=`average rank`)
)

imffr3<-left_join(imffr2,index2,by=c("monitoring","formalenforcement","legalbasis","coverage"))%>%
  mutate(frsi=10*(max(av_rank)-av_rank)/(max(av_rank)-min(av_rank)))%>%
  select(1:5,11)%>%
  pivot_wider(names_from =c(level,ruletype),values_from = frsi,names_prefix = "frsi_" )
  
saveRDS(imffr3,"dfs/imffr3")

eval<-imffr3%>%
  select(matches("_national_"))%>%
  pop2prof()%>%
  evaluation(threshold = "0000", error = 10^(-3))

saveRDS(eval,"dfs/eval")

eval<-readRDS("dfs/eval")
s_eval<-eval%>%summary()%>%select(matches("frsi"),"frsi_national_full"="average rank")%>%mutate(frsi_national_full=10*(max(frsi_national_full)-frsi_national_full)/(max(frsi_national_full)-min(frsi_national_full)))

imffr4<-left_join(imffr3,s_eval,by=c("frsi_national_er","frsi_national_rr","frsi_national_bbr","frsi_national_dr"))

eval2<-imffr3%>%
  select(matches("_supranational_"))%>%
  pop2prof()%>%
  evaluation(threshold = "0000", error = 10^(-3))

saveRDS(eval2,"dfs/eval2")

eval2<-readRDS("dfs/eval2")
s_eval2<-eval2%>%summary()%>%select(matches("frsi"),"frsi_supranational_full"="average rank")%>%mutate(frsi_supranational_full=10*(max(frsi_supranational_full)-frsi_supranational_full)/(max(frsi_supranational_full)-min(frsi_supranational_full)))

frsi<-left_join(imffr4,s_eval2,by=c("frsi_supranational_er","frsi_supranational_rr","frsi_supranational_bbr","frsi_supranational_dr"))
saveRDS(frsi,"dfs/frsi")

frsi<-readRDS("dfs/frsi")%>%mutate(region=countrycode(countrycode,"iso3c","un.region.name",custom_match = c("XXK"="Europe")))
```

# Dependent variable
```{r eval=FALSE, include=FALSE}
data_cofog<-read_delim("Data/Cofog1985.csv",delim=";")%>%
  select(countrycode=LOCATION,tran=TRANSACT,fun=Function,year=Year,value=Value)%>%
  filter(tran%in%c("TLYCG","P5CG"))%>%
  mutate(region=countrycode(countrycode,"iso3c","un.region.name"))%>%
  pivot_wider(names_from = tran,values_from = value)%>%
  mutate(ratio_inv_exp=100*P5CG/TLYCG,
         investment=P5CG,
         expenditure=TLYCG)%>%
 # select(-c(P5CG,TLYCG))%>%
  filter(fun=="Total function",year>=1995)
```

# Controls

## Database of Political Institutions

```{r,eval=FALSE eval=FALSE, include=FALSE, r,eval=FALSE}
data_dpi<-read_dta("Data/DPI2020.dta")%>%
  dplyr::select(countrycode=ifs,year,legelec,exelec)%>%

  mutate(across(where(is.numeric),~as.numeric(.),.names = "{.col}"),
         across(where(is.numeric), ~case_when(.==-999~NA_real_,
                                       TRUE~.),.names = "{.col}"),
         across(where(is.character),~as.character(.),.names = "{.col}"),
         across(where(is.character), ~case_when(.=="-999"~NA_character_,
                                              TRUE~.),.names = "{.col}"))%>%
  rename_with(~gsub("(.*)","control_\\1",.)%>%tolower(),-c(countrycode,year))%>%
  select(countrycode,year,control_legelec,control_exelec)



saveRDS(data_dpi,"dfs/dpi")
data_dpi<-readRDS("dfs/dpi")
```

## AMECO (European Comission)

UDGGL= Debt GG (Percentage of GDP at current prices (excessive deficit procedure)) 
UVGD= GDP current prices (Mrd ECU/EUR) AVGDGP= output gap (Percentage of potential gross domestic product at constant prices) 
UYIG= interest: general government (Percentage of GDP at current prices (excessive deficit procedure)) 
UBLGI= net deficit excluding interest (Percentage of GDP at current prices (excessive deficit procedure))

```{r eval=FALSE, include=FALSE}
series<-c("UDGGL","UVGD","AVGDGP","UYIG","UBLGI")
api_link<-paste0("https://api.db.nomics.world/v22/series/AMECO/",series,"?observations=1")

data_ameco<-lapply(api_link,function(x){
  rdb(api_link = x) 
})%>%do.call("rbind",.)%>%
  filter(
         (dataset_code=="UDGGL"&Unit=="(Percentage of GDP at current prices (excessive deficit procedure))")|
           (dataset_code=="UVGD"&Unit=="Mrd ECU/EUR")|
           (dataset_code=="AVGDGP"&Unit=="(Percentage of potential gross domestic product at constant prices)")|
           (dataset_code=="UYIG"&Unit=="(Percentage of GDP at current prices (excessive deficit procedure))")|
           (dataset_code=="UBLGI"&Unit=="(Percentage of GDP at current prices (excessive deficit procedure))")
         
         )%>%
  select(countrycode=geo,country=Country,variable=dataset_code,year=original_period,value)%>%
  mutate(countrycode=countrycode(countrycode,"iso3c","iso3c",custom_match = c("ROM"="ROU")),year=as.numeric(year))%>%
  filter(!is.na(countrycode))%>%
  pivot_wider(c(countrycode,country,year),names_from = variable,names_prefix = "control_",values_from = value)
```

```{r eval=FALSE, include=FALSE}
data<-left_join(data_cofog,frsi,by=c("countrycode","year","region"))%>%
  left_join(data_ameco,by=c("countrycode","year","countryname"="country"))%>%
  left_join(data_dpi,by=c("countrycode","year"))%>%
 # filter(year%in%1995:2021,region=="Europe")%>%
  mutate(log_exp=log(expenditure),
         log_inv=log(investment))%>%
  select(countrycode,countryname,3:7,log_inv,log_exp,everything(),-fun)

saveRDS(data,"dfs/data")
```

# Regressions

```{r}
data<-readRDS("dfs/data")
controls<-c("control_AVGDGP","control_UDGGL","control_UVGD","control_UBLGI","control_UYIG","control_legelec","control_exelec")
window<-c(-5,5)
outcome_lags<-4
nonabsorbing_lag<-5
```

## full

```{r}
reg_full_ratio<-lpdid(data, window = window,
             y="ratio_inv_exp",
             exp_var = "frsi_national_full",
            controls = controls,
             unit_index = "countrycode",
             time_index = "year",
             outcome_lags = outcome_lags,
             reweight = FALSE,
             nonabsorbing = TRUE,
             nonabsorbing_lag = nonabsorbing_lag)

reg_full_exp<-lpdid(data, window = window,
             y="log_exp",
             exp_var = "frsi_national_full",
              controls = controls,
             unit_index = "countrycode",
             time_index = "year",
             outcome_lags = outcome_lags,
             reweight = FALSE,
             nonabsorbing = TRUE,
             nonabsorbing_lag = nonabsorbing_lag)

reg_full_inv<-lpdid(data, window = window,
             y="log_inv",
             exp_var = "frsi_national_full",
             controls = controls,
             unit_index = "countrycode",
             time_index = "year",
             outcome_lags = outcome_lags,
             reweight = FALSE,
             nonabsorbing = TRUE,
             nonabsorbing_lag = nonabsorbing_lag)


vis_reg_full_ratio<-reg_full_ratio%>%plot_lpdid(title = "Investment-to-expenditure ratio",ymin=-.4,ymax=.2)
vis_reg_full_inv<-reg_full_inv%>%plot_lpdid(title = "Investment",loglin =TRUE,ymin=-.06,ymax=.02)
vis_reg_full_exp<-reg_full_exp%>%plot_lpdid(title = "Expenditure",loglin = TRUE,ymin=-.06,ymax=.02)

vis_full<-vis_reg_full_ratio/
(vis_reg_full_inv+
vis_reg_full_exp)
vis_full

save_vis(vis_full,"vis_full",path = f_graphics,height = 25,width=30)
```

## BBR

```{r}

reg_bbr_ratio<-lpdid(data, window = window,
             y="ratio_inv_exp",
             exp_var = "frsi_national_bbr",
            controls = controls,
             unit_index = "countrycode",
             time_index = "year",
             outcome_lags = outcome_lags,
             reweight = FALSE,
             nonabsorbing = TRUE,
             nonabsorbing_lag = nonabsorbing_lag)

reg_bbr_exp<-lpdid(data, window = window,
             y="log_exp",
             exp_var = "frsi_national_bbr",
              controls = controls,
             unit_index = "countrycode",
             time_index = "year",
             outcome_lags = outcome_lags,
             reweight = FALSE,
             nonabsorbing = TRUE,
             nonabsorbing_lag = nonabsorbing_lag)

reg_bbr_inv<-lpdid(data, window = window,
             y="log_inv",
             exp_var = "frsi_national_bbr",
             controls = controls,
             unit_index = "countrycode",
             time_index = "year",
             outcome_lags = outcome_lags,
             reweight = FALSE,
             nonabsorbing = TRUE,
             nonabsorbing_lag = nonabsorbing_lag)


vis_reg_bbr_ratio<-reg_bbr_ratio%>%plot_lpdid(title = "Investment-to-expenditure ratio",ymin=-.3,ymax=.1)
vis_reg_bbr_exp<-reg_bbr_exp%>%plot_lpdid(title = "Expenditure",loglin = TRUE,ymin=-.04,ymax=.02)
vis_reg_bbr_inv<-reg_bbr_inv%>%plot_lpdid(title = "Investment",loglin =TRUE,ymin=-.04,ymax=.02)

vis_bbr<-vis_reg_bbr_ratio/
(vis_reg_bbr_inv+
vis_reg_bbr_exp)
vis_bbr

save_vis(vis_bbr,"vis_bbr",path = f_graphics,height = 25,width=30)
```

## DR

```{r}


reg_dr_ratio<-lpdid(data, window = window,
             y="ratio_inv_exp",
             exp_var = "frsi_national_dr",
            controls = controls,
             unit_index = "countrycode",
             time_index = "year",
             outcome_lags = outcome_lags,
             reweight = FALSE,
             nonabsorbing = TRUE,
             nonabsorbing_lag = nonabsorbing_lag)

reg_dr_exp<-lpdid(data, window = window,
             y="log_exp",
             exp_var = "frsi_national_dr",
              controls = controls,
             unit_index = "countrycode",
             time_index = "year",
             outcome_lags = outcome_lags,
             reweight = FALSE,
             nonabsorbing = TRUE,
             nonabsorbing_lag = nonabsorbing_lag)

reg_dr_inv<-lpdid(data, window = window,
             y="log_inv",
             exp_var = "frsi_national_dr",
             controls = controls,
             unit_index = "countrycode",
             time_index = "year",
             outcome_lags = outcome_lags,
             reweight = FALSE,
             nonabsorbing = TRUE,
             nonabsorbing_lag = nonabsorbing_lag)


vis_reg_dr_ratio<-reg_dr_ratio%>%plot_lpdid(title = "Investment-to-expenditure ratio",ymin=-.4,ymax=.4)
vis_reg_dr_exp<-reg_dr_exp%>%plot_lpdid(title = "Expenditure",loglin = TRUE,ymin=-.04,ymax=.04)
vis_reg_dr_inv<-reg_dr_inv%>%plot_lpdid(title = "Investment",loglin =TRUE,ymin=-.04,ymax=.04)

vis_dr<-vis_reg_dr_ratio/
(vis_reg_dr_inv+
vis_reg_dr_exp)
vis_dr

save_vis(vis_dr,"vis_dr",path = f_graphics,height = 25,width=30)
```

## ER

```{r}


reg_er_ratio<-lpdid(data, window = window,
             y="ratio_inv_exp",
             exp_var = "frsi_national_er",
            controls = controls,
             unit_index = "countrycode",
             time_index = "year",
             outcome_lags = outcome_lags,
             reweight = FALSE,
             nonabsorbing = TRUE,
             nonabsorbing_lag = nonabsorbing_lag)

reg_er_exp<-lpdid(data, window = window,
             y="log_exp",
             exp_var = "frsi_national_er",
              controls = controls,
             unit_index = "countrycode",
             time_index = "year",
             outcome_lags = outcome_lags,
             reweight = FALSE,
             nonabsorbing = TRUE,
             nonabsorbing_lag = nonabsorbing_lag)

reg_er_inv<-lpdid(data, window = window,
             y="log_inv",
             exp_var = "frsi_national_er",
             controls = controls,
             unit_index = "countrycode",
             time_index = "year",
             outcome_lags = outcome_lags,
             reweight = FALSE,
             nonabsorbing = TRUE,
             nonabsorbing_lag = nonabsorbing_lag)

vis_reg_er_ratio<-reg_er_ratio%>%plot_lpdid(title = "Investment-to-expenditure ratio",ymin=-.2,ymax=.2)
vis_reg_er_exp<-reg_er_exp%>%plot_lpdid(title = "Expenditure",loglin = TRUE,ymin=-.04,ymax=.04)
vis_reg_er_inv<-reg_er_inv%>%plot_lpdid(title = "Investment",loglin =TRUE,ymin=-.04,ymax=.04)

vis_er<-vis_reg_er_ratio/
(vis_reg_er_inv+
vis_reg_er_exp)
vis_er

save_vis(vis_er,"vis_er",path = f_graphics,height = 25,width=30)
```

# Visualisations
## investment-to-expenditure ratio
```{r}
data_depvar<-cofog2%>%
  mutate(year_group=case_when(year<2000~"1995-1999",
                              year<2005~"2000-2004",
                              year<2010~"2005-2009",
                              year<2015~"2010-2014",
                              TRUE~"2016-2021"))
  


 vis_invexp_ratio<- data_depvar%>%
    ggplot(aes(x=year_group,y=ratio_inv_exp))+
       ggbeeswarm::geom_quasirandom(shape = 21,size=2, dodge.width = .75,width=0.35,show.legend = T,varwidth = T,color="#ee6174",fill="#ee6174")+
    geom_point(aes(y=mean),data=data_depvar%>%group_by(year_group)%>%summarise(mean=mean(ratio_inv_exp,na.rm = T)),size=3)+
  labs(x=NULL,y=NULL,fill=NULL,color=NULL)+
  scale_y_continuous(limits = c(0,30))+
  theme_tufte(base_family = "lmroman",base_size = 20)+
  theme(axis.text.x = element_text(angle = 90),
        axis.text.y = element_text(),
        panel.grid.major.y = element_line(linetype = "dotted"),
        axis.ticks = element_blank(),
        axis.line = element_blank(),
        panel.spacing = unit(0,"lines"),legend.position="none")

ggsave("vis_invexp_ratio.pdf", vis_invexp_ratio, device = "pdf", height = 15, width = 30, 
    units = "cm", path = f_graphics)

data_depvar%>%group_by(year_group)%>%summarise(mean=mean(ratio_inv_exp,na.rm = T))
```

## frsi
```{r}
data_trend<-frsi%>%
  #filter(region=="Europe")%>%
  mutate(frsi_national_full2=case_when(frsi_national_full==0~NA_real_,
                                 TRUE~frsi_national_full
                                 ))%>%
  group_by(year)%>%
  summarise(
    number_fiscalrules=sum(frsi_national_full!=0),
    frsi_national_full=mean(frsi_national_full2,na.rm=T))


vis1<-data_trend%>%
  ggplot(aes(x=year))+
  geom_col(aes(y=number_fiscalrules),fill="#51275f",color="#51275f",width = 0.6)+
  #geom_line(aes(y=frsi_national_full*10),size=2,color="#ee6174")+
  scale_x_continuous(expand = c(0,0),breaks = 1985+0:7*5)+
  scale_y_continuous(limits = c(0,100))+
  labs(title="Number of fiscal rules",x=NULL,y=NULL)+
  theme_tufte(base_size = 20,base_family = "lmroman")+
  theme(axis.text.x = element_text(angle = 90),
        axis.text.y = element_text(),
        panel.grid.major.y = element_line(linetype = "dotted"),
        axis.ticks = element_blank(),
        axis.line.y = element_blank(),
        axis.line.x = element_blank(),
        panel.spacing = unit(0,"lines"))

vis2<-data_trend%>%
  ggplot(aes(x=year))+
 # geom_col(aes(y=number_fiscalrules),fill="#51275f",color="#51275f",width = 0.8)+
  geom_col(aes(y=frsi_national_full),color="#ee6174",fill="#ee6174",width = 0.6)+
  scale_x_continuous(expand = c(0,0),breaks = 1985+0:7*5)+
  scale_y_continuous(limits = c(0,10))+
  labs(title="Fiscal rules index",x=NULL,y=NULL)+
  theme_tufte(base_size = 20,base_family = "lmroman")+
  theme(axis.text.x = element_text(angle = 90),
        axis.text.y = element_text(),
        panel.grid.major.y = element_line(linetype = "dotted"),
        axis.ticks = element_blank(),
        axis.line.y = element_blank(),
        axis.line.x = element_blank(),
        panel.spacing = unit(0,"lines"))

frsi_trend<-vis1+vis2
frsi_trend

ggsave("frsi_trend.pdf", frsi_trend, device = "pdf", height = 15, width = 30,
    units = "cm", path =f_graphics)
```

# Tables
```{r}
data05<-data%>%
  dplyr::filter(year%in%c(1995,2000,2005,2010,2015,2016,2017))




id_vars<-c("countrycode","countryname","year","region")
controls<-data%>%select(matches("control_"))%>%names()

data_used<-data%>%
  select(all_of(id_vars),ratio_inv_exp,investment,expenditure,log_inv,log_exp,matches("^frsi"),all_of(controls))
data_used05<-data05%>%
  select(all_of(id_vars),ratio_inv_exp,log_inv,log_exp,investment,expenditure,matches("^frsi"),matches("^frsi"),all_of(controls))


data_explanatory<-data%>%
  select(year,matches("^frsi"))
data_explanatory05<-data05%>%
  select(year,matches("^frsi"))


data_dependent<-data%>%
  select(year,ratio_inv_exp,investment,expenditure,log_inv,log_exp)
data_dependent05<-data05%>%
  select(year,ratio_inv_exp,investment,expenditure,log_inv,log_exp)


data_controls<-data%>%
  select(year,all_of(controls))
data_controls05<-data05%>%
  select(year,all_of(controls))

data_list<-list("Explanatory Variables"=data_explanatory,"Dependent Variables"=data_dependent,"Control Variables"=data_controls)

data_list05<-list("Explanatory Variables"=data_explanatory05,"Dependent Variables"=data_dependent05,"Control Variables"=data_controls05)
```

```{r}
myDescriptives <- function(x) {
    x = as.numeric(x)
    m = mean(x, na.rm = TRUE)
    md = median(x, na.rm = TRUE)
    sd = sd(x, na.rm = TRUE)
    x25 = quantile(x,probs=0.25,na.rm=TRUE)
    x75 = quantile(x,probs=0.75,na.rm=TRUE)
    IQR = IQR(x,na.rm = TRUE)
    
  return(c(m, md, sd,x25,x75,IQR))
}

myDescriptives_group <- function(x) {
    x = as.numeric(x)
    m = mean(x, na.rm = TRUE)
    md = median(x, na.rm = TRUE)
    sd = sd(x, na.rm = TRUE)
    
  return(c(m,sd))
}
```

```{r}
#https://cran.r-project.org/web/packages/reporttools/vignettes/reporttools.pdf
#https://sdaza.com/blog/2020/descriptive-tables/
#describe(data_controls%>%select(-all_of(id_vars)))
expl_vars<-c("frsi_national_full","frsi_national_bbr","frsi_national_dr","frsi_national_er")
expl_labels<-c("frsi-national-full","frsi-national-bbr","frsi-national-dr","frsi-national-er")

dep_vars<-c("ratio_inv_exp","log_inv","log_exp")

dep_labels<-c("ratio-inv-exp","log-inv","log-exp")

control_labels<-c("UDGGL","UVGD","AVGDGP","UYIG","UBLGI","legelec","exelec")


variables = list(expl_vars, dep_vars, controls)
labels = list(expl_labels, dep_labels, control_labels)
colnames =  c("Mean", "Median", "SD","$Q_1$","$Q_3$","IQR")
colnames_grouped =  c("Mean", "SD")
path<-"C:/Users/leona/Dropbox/Apps/Overleaf/Fiscal Rules Budget Composition/Tables/"

createDescriptiveTable(datasets = data_list,
    summary_function = myDescriptives,
    column_names = colnames,
    variable_names = variables,
    variable_labels = labels,
    arraystretch = 1.3,
    title = "Descriptive statistics",
    label = "tab:descriptive",
    file = paste0(path,"/descriptive1.tex"))

createDescriptiveTable(data_list05,
    summary_function = myDescriptives_group,
    column_names = colnames_grouped,
    variable_names = variables,
    group_variable = "year",
    variable_labels = labels,
    arraystretch = 1.3,
    title = "Descriptive statistics",
    label = "tab:descriptive",
    file = paste0(path,"/descriptive_grouped.tex"),
    fontsize = "\\fontsize{7pt}{8pt}\\selectfont")
```



# Quick numbers
```{r}

data%>%
  group_by(year)%>%
  summarise(
    number_fiscalrules=sum(frsi_national_bbr!=0,na.rm = T))%>%
  filter(year==1995|
         year==2021)

data%>%
  group_by(year)%>%
  summarise(
    number_fiscalrules=sum(frsi_national_dr!=0,na.rm = T))%>%
  filter(year==1995|
         year==2021)

data%>%
  group_by(year)%>%
  summarise(
    number_fiscalrules=sum(frsi_national_er!=0,na.rm = T))%>%
  filter(year==1995|
         year==2021)

frsi%>%
  group_by(year)%>%
  summarise(
    number_fiscalrules=sum(frsi_national_rr!=0))%>%
  filter(year==1995|
         year==2021)
```

```{r}
data$frsi_national_full%>%sd(na.rm = T)

data$ratio_inv_exp%>%mean(na.rm = T)

frsi$countrycode%>%unique()%>%length()
```

```{r}
reg_full_ratio$coeftable$Estimate
reg_full_inv$coeftable$Estimate*100
reg_full_exp$coeftable$Estimate*100

reg_bbr_ratio$coeftable$Estimate
reg_bbr_inv$coeftable$Estimate*100
reg_bbr_exp$coeftable$Estimate*100

reg_dr_ratio$coeftable$Estimate
reg_dr_inv$coeftable$Estimate*100
reg_dr_exp$coeftable$Estimate*100

reg_er_ratio$coeftable$Estimate
reg_er_inv$coeftable$Estimate
reg_er_exp$coeftable$Estimate

```